Macro Impacts

### 2016-08-03 Macro Impacts Revised.tex
update
Update

\f{E_m'}{N} &= \f{p_0^2}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\

@@

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = f\times (b^2-a^2)$. If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$. When $T$ is zero, we get the result from section 2, which goes approximately as $k_0^2$. A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value. This constant value is achieved slower for larger $Q$ (or smaller $T$). In essence, this shows how the higher frequency terms stop contributing, and the small $k$ terms dominate.

@@

\pagebreak
\section{Thermal Source}
A simple model for seismic wave generation via macro impact is that a cylinder is heated uniformly. Since we are interested in an upper bound to seismic energy generation, it is reasonable to find the optimal volume (i.e. radius) and temperature for maximal thermal expansion and minimal energy lost to heating. Since the energy lost to heating corresponds to the energy lost in melting, the second requirement is equivalent to minimizing volume...

\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.

>>>>

\f{E_m'}{N} &= \f{1}{N}\f{\lambda_m+2\mu_m}{K_m^2}F_{m,n}^2\int\f{\diff^3 k}{(2\pi)^3}\abs{\f{4\pi p_0}{k\cos\theta}\sin\p{\f{h k\cos\theta}{2}}(b^2f_1(b)-a^2f_1(a))}^2e^{-k\f{T_{m,n}}{Q_{m,n}}}\,,\\

@@

$A$ is a constant which characterizes the explosion for small $k$. In the case that $f$ is constant, $A = f\times (b^2-a^2)$. If $f$ is the triangle from section 2, then $A = \f16\Delta r(3r_0 + 2\Delta r)$. When $T$ is zero, we get the result from section 2, which goes approximately as $k_0^2$. A quick plot of $E_m'$ shows that it goes as $k_0^2$ for small $k_0$ but asymptotes to a constant value (more precisely, it goes as the expression in section 2). This constant value is achieved slower for larger $Q$ (or smaller $T$). In essence, this shows how the higher frequency terms stop contributing, and the small $k$ terms dominate. Note that $Q$ is on the order of $10^2$ or $10^3$, while $T$ is likely on the order of $10^3$ (seconds).
In the case that $\f{T}{Q}\gg 1$, then $k_0\to\infty$ is close to the actual value. In this case, the limit is just
E_m'\leq F_{m,n}^24 l p_0^2 \f{Q^2}{T^2} \arctan\ps{l\f{Q}{T}} A\rho_m2l^2\sigma_Xv_X^2\,.
Unfortunately, this approximation does not hold for rays originating near the surface (which always exist for our line source), since $Q_p$ near the surface is large and $T$ is small. In this case, we can use the expression from section 1. But when our computers are super fast, why approximate?
Now, for a ray that immediately hits the surface, its energy must be the same as when it started. This corresponds to $T = \to 0$, and
E_m = 4l E_mAF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}
where we've taken $l\rho_m\sigma_Xv_X^2=E_m$.
 \p{4lF_{m,n}^2\p{-2k_0+k_0\cos(h k_0)+\f{\sin(h k_0)}{h}+h k_0^2\te{Si}(h k_0)}}^{-1}=  A
These units are way wrong. Gonna fix tomorrow.

@@

\pagebreak
\section{Thermal Source}
A simple model for seismic wave generation via macro impact is that a cylinder is heated uniformly. Since we are interested in an upper bound to seismic energy generation, it is reasonable to find the optimal volume (i.e. radius) and temperature for maximal thermal expansion and minimal energy lost to heating. Since the energy lost to heating corresponds to the energy lost in melting, the second requirement is equivalent to minimizing volume... 
\pagebreak
\section{Melt Zone}
As derived in ''A time dependent model for long-rod penetration" the plastic zone (i.e. the melt zone) around an impacting projectile is given by $\alpha*R$, where $\alpha$ is given by 
\begin{align}
(1+\frac{\rho_t u^2}{Y_t})\sqrt{K_t - \rho_t \alpha^2 u^2} = (1+\frac{\rho_t \alpha^2 u^2}{2G_t})\sqrt{K_t - \rho_t u^2}.
\end{align}
where $u$ is the velocity of the projectile (i.e. the macro), $\rho_t$, $K_t$, $G_t$ and $Y_t$ are the density, bulk modulus, sheer modulus, and flow stress of the target (i.e. earth or the moon) respectively.
